Microxanox: an R package for simulating an aquatic \(MICR\)obial ecosystem that can occupy \(OX\)ic or \(ANOX\)ic states.

### 2023-06-12 inst/manuscript/manuscript_microxanox.Rmd
Revised Submission

The framework used when writing this package aimed to maximise simplicity for the user and to make it straightforward to reproduce results (see the supplement [@Petchey2022] to @Limberger2023 for an example of how this is used, and XXXXX). As such, all the parameters needed to run a simulation or a set of simulations are contained in a single object (which can easily be created using included functions). This parameter object is given to a function that runs the simulations and returns the results. The returned results object is identical to the parameter object but with an additional slot named `results`, which contains the simulation results. Thus the returned results object contains the simulation conditions (parameters) as well as the results, and can be used to run the simulation again. This promotes reproducibility and makes incremental changes of individual parameters with a consecutive re-running of the simulations straightforward.

@@

The design of the package code and functionality is with reproducibility in mind (for other example of reproducibility directed software, see e.g. @Correndo2023, @Spillner2022or @Fox2020): the combination of all parameters being in a single parameter object and the return of the simulation as a result object which inherits from the parameter object, provides a relatively easy-to-use framework to implement reproducible experiments.

@@

As discussed in the Introduction section, the package was motivated by the question of how biodiversity influences ecosystem responses to environmental change. Extensive results concerning this question are given in a separate publication @Limberger2023. Here we describe one of the results, which is that having biodiversity in a functional group can allow state changes to occur that otherwise would not have. I.e. biodiversity can qualitatively change the state of the ecosystem.

>>>>

The framework used when writing this package aimed to maximise simplicity for the user and to make it straightforward to reproduce results (see the supplement [@Petchey2022] to @Limberger2023 for an example of how this is used). As such, all the parameters needed to run a simulation or a set of simulations are contained in a single object (which can easily be created using included functions). This parameter object is given to a function that runs the simulations and returns the results. The returned results object is identical to the parameter object but with an additional slot named `results`, which contains the simulation results. Thus the returned results object contains the simulation conditions (parameters) as well as the results, and can be used to run the simulation again. This promotes reproducibility and makes incremental changes of individual parameters with a consecutive re-running of the simulations straightforward.

@@

The design of the package code and functionality is with reproducibility in mind (for other example of reproducibility directed software, see e.g. @Correndo2023, @Spillner2022 or @Fox2020): the combination of all parameters being in a single parameter object and the return of the simulation as a result object which inherits from the parameter object, provides a relatively easy-to-use framework to implement reproducible experiments.

@@

As discussed in the Introduction section, the package was motivated by the question of how biodiversity influences ecosystem responses to environmental change. Extensive results concerning this question are given in a separate publication @Limberger2023. Here we describe one of the results, which is that having biodiversity in a functional group can allow state changes to occur that otherwise would not have, i.e. biodiversity can qualitatively change the state of the ecosystem.

### 2023-06-12 inst/manuscript/manuscript_microxanox.tex
Revised Submission

The framework used when writing this package aimed to maximise simplicity for the user and to make it straightforward to reproduce results (see the supplement \citep{Petchey2022} to \citet{Limberger2023} for an example of how this is used, and XXXXX). As such, all the parameters needed to run a simulation or a set of simulations are contained in a single object (which can easily be created using included functions). This parameter object is given to a function that runs the simulations and returns the results. The returned results object is identical to the parameter object but with an additional slot named \texttt{results}, which contains the simulation results. Thus the returned results object contains the simulation conditions (parameters) as well as the results, and can be used to run the simulation again. This promotes reproducibility and makes incremental changes of individual parameters with a consecutive re-running of the simulations straightforward.

@@

The design of the package code and functionality is with reproducibility in mind (for other example of reproducibility directed software, see e.g. \citet{Correndo2023}, \citet{Spillner2022or} \citet{Fox2020}): the combination of all parameters being in a single parameter object and the return of the simulation as a result object which inherits from the parameter object, provides a relatively easy-to-use framework to implement reproducible experiments.

@@

As discussed in the Introduction section, the package was motivated by the question of how biodiversity influences ecosystem responses to environmental change. Extensive results concerning this question are given in a separate publication \citet{Limberger2023}. Here we describe one of the results, which is that having biodiversity in a functional group can allow state changes to occur that otherwise would not have. I.e. biodiversity can qualitatively change the state of the ecosystem.

>>>>

The framework used when writing this package aimed to maximise simplicity for the user and to make it straightforward to reproduce results (see the supplement \citep{Petchey2022} to \citet{Limberger2023} for an example of how this is used). As such, all the parameters needed to run a simulation or a set of simulations are contained in a single object (which can easily be created using included functions). This parameter object is given to a function that runs the simulations and returns the results. The returned results object is identical to the parameter object but with an additional slot named \texttt{results}, which contains the simulation results. Thus the returned results object contains the simulation conditions (parameters) as well as the results, and can be used to run the simulation again. This promotes reproducibility and makes incremental changes of individual parameters with a consecutive re-running of the simulations straightforward.

@@

The design of the package code and functionality is with reproducibility in mind (for other example of reproducibility directed software, see e.g. \citet{Correndo2023}, \citet{Spillner2022} or \citet{Fox2020}): the combination of all parameters being in a single parameter object and the return of the simulation as a result object which inherits from the parameter object, provides a relatively easy-to-use framework to implement reproducible experiments.

@@

As discussed in the Introduction section, the package was motivated by the question of how biodiversity influences ecosystem responses to environmental change. Extensive results concerning this question are given in a separate publication \citet{Limberger2023}. Here we describe one of the results, which is that having biodiversity in a functional group can allow state changes to occur that otherwise would not have, i.e.~biodiversity can qualitatively change the state of the ecosystem.
